RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

# Gene set analysis
```{r zenith.celltype, cache=FALSE, eval=FALSE}

geneSets_GO = get_GeneOntology()

filter_gs = function(fit, gs){
  # Map from Ensembl genes in geneSets_GO to 
  # Ensembl names from RNA-seq data 
  index = ids2indices( recodeToList(gs), rownames(fit))

  # filter by size of gene set
  n_genes_in = 15
  setSize = sapply(index, length)
  idxGO = index[(setSize > n_genes_in) & (setSize < 500)]
  idxGO
}

fit = fitBasic[fitBasic$Amean > -Inf,]
idxGO = filter_gs( fit, geneSets_GO)

df_CT_zenith = lapply( colnames(coef(fitBasic)), function(key){
  res = zenith( fit, coef = key, index = idxGO, inter.gene.cor=0.01)
  data.table(Geneset = rownames(res), res, coef = key)
})
df_CT_zenith = do.call(rbind, df_CT_zenith)

df_gs = lapply( df_CT_zenith[,unique(coef)], function(key){

  # results for this coef
  df_sub = df_CT_zenith[(coef == key),][order(p.greater),]

  # remove gene sets with small p-values from other tests
  df_sub2 = df_CT_zenith[(coef != key),][order(p.greater),]
  df_sub2 = df_sub2[,.SD[which.min(p.greater),], by="Geneset"]
  df_sub2 = df_sub2[p.greater > 1e-3,]

  df_sub[!(df_sub$Geneset %in% df_sub2$Geneset),][1:4,]
  })
df_gs = do.call(rbind, df_gs)

df_gs %>% kable() %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)

df = df_gs[grep("CellType", coef),]
# df = rbind(df, df_gs[grep('GABAGLU_vs_Other|GABA_vs_GLU', coef)])
df[,coef := gsub("CellType", '',coef)]
df$coef = factor(df$coef, names(colorCodes))

ggplot(df, aes(Geneset,coef, -log10(p.greater))) + geom_tile() + coord_flip() + scale_y_continuous(expand=c(0,0)) + theme_classic() + ylab(bquote(-log[10]~p)) + scale_fill_manual(values = c(colorCodes, GABAGLU_vs_Other = "green"), name="Cell type") 
```

```{r compare.celltypes, fig.width=8, fig.height=12}
zenith_gsa = function (fit, coefs, geneSets, n_genes_min = 10, n_genes_max=1000,...){

@@

coefTests = c('GABA_vs_GLU', 'GABAGLU_vs_Other', 'GLU_vs_Other', 'GABA_vs_Other', 'MgAs_vs_Other', 'Olig_vs_Other')
df_zenith = zenith_gsa(fitBasic[fitBasic$Amean > 0,], coefTests, geneSets_GO)
#, inter.gene.cor=0.01)

@@

```{r eval=FALSE}
# form = ~ CellType + Gender + Batch

# idx = info$CellType %in% c("Olig", "GABA")
# isexpr = filterByExpr(geneCounts[,idx], model.matrix(~CellType, info[idx,]))
# dge = DGEList(geneCounts[isexpr,idx])
# dge = calcNormFactors(dge)
# vobj = voom(dge, model.matrix(~CellType, droplevels(info[idx,])))

# fit = lmFit( vobj, model.matrix(form, droplevels(info[idx,])))
# fit = eBayes(fit)
# fit = dream(vobj, form, info[idx,])
# fit = eBayes(fit)
# res2 = zenith(fit, coef='CellTypeOlig',idxGO )

# # Map from Ensembl genes in geneSets_GO to 
# # Ensembl names from RNA-seq data 
# index = ids2indices( recodeToList(geneSets_GO), rownames(fit))

# n_genes_in = 20
# idxGO = index[sapply(index, length) > n_genes_in]

# res = camera( vobj, idxGO, model.matrix(form, droplevels(info[idx,])), inter.gene.cor=NA, contrast='CellTypeOlig')

>>>>

# Gene set analysis
```{r compare.celltypes, fig.width=8, fig.height=12}
zenith_gsa = function (fit, coefs, geneSets, n_genes_min = 10, n_genes_max=1000,...){

@@

coefTests = c('GABA_vs_GLU', 'GABAGLU_vs_Other', 'GLU_vs_Other', 'GABA_vs_Other', 'MgAs_vs_Other', 'Olig_vs_Other')
df_zenith = zenith_gsa(fitBasic[fitBasic$Amean > 0,], coefTests, geneSets_GO, inter.gene.cor=0.01)

@@
